Modal Abstractions for Virtualizing Memory Addresses

### 2023-11-16 programlogic.tex
+

\begin{figure}
\begin{mathpar}
  \inferrule[WriteToRegFromReg]{
  \{P \ast r_d \mapsto_{r} \textsf{rvs} \ast r_s \mapsto_{r}\{q\} \textsf{ rvs} \}_{\textsf{rtv}}\;\overline{ is}
}{
  \{P \ast r_d \mapsto_{r} \textsf{rvd} \ast r_s \mapsto_{r}\{q\} \textsf{ rvs} \}_{\textsf{rtv}}
  \textsf{ mov}~\textsf{r}_d,~\textsf{r}_s;\;\overline{is}
  %\lstinline|mov %cr3, r| 
}
\\
% \inferrule[WriteToPhysMemFromReg]{
%   \{P \ast r_s \mapsto_{r}\{q\}  \textsf{rvs}  \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{t}} \textsf{v} \}_{\textsf{rtv}}\;\overline{ is}  
% }{
%   \{P \ast r_s \mapsto_{r}\{q\}  \textsf{rvs}   \ast r_a \mapsto_{r}\{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{t}} \textsf{rvs} \}_{\textsf{rtv}}
%   \textsf{ mov}~[\textsf{r}_a],~\textsf{r}_s;\;\overline{is}
% }
% \\
% \inferrule[WriteToRegFromPhysMem]{
%   \{P \ast r_d \mapsto_{r}  \textsf{v} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{t}} \textsf{v} \}_{\textsf{rtv}}\;\overline{is}
% }{
%   \{P \ast r_d \mapsto_{r}  \textsf{rvd} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{t}} \textsf{v} \}_{\textsf{rtv}}
%   \textsf{mov}~\textsf{r}_d,~[\textsf{r}_a];\;\overline{is}
% }
% \\
\inferrule[WriteToRegFromVirtMem]{
  \{P \ast \mathcal{I}\textsf{ASpace}\ast \mathcal{I}\textsf{ASpace} \ast r_d \mapsto_{r}  \textsf{v} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{v} \}_{\textsf{rtv}}\;\overline{is}
}{
  \{P \ast \mathcal{I}\textsf{ASpace}\ast r_d \mapsto_{r}  \textsf{rvd} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{v} \}_{\textsf{rtv}}
  \textsf{mov}~\textsf{r}_d,~[\textsf{r}_a];\;\overline{is}
}
\\
\inferrule[WriteToVirtMemFromReg]{
  \{P \ast \mathcal{I}\textsf{ASpace}\ast r_s \mapsto_{r}\{q\}  \textsf{rvs}  \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{v} \}_{\textsf{rtv}}\;\overline{ is}  
}{
  \{P \ast \mathcal{I}\textsf{ASpace}\ast r_s \mapsto_{r}\{q\}  \textsf{rvs}   \ast r_a \mapsto_{r}\{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{rvs} \}_{\textsf{rtv}}
  \textsf{ mov}~[\textsf{r}_a],~\textsf{r}_s;\;\overline{is}
}
\\
\inferrule[WriteToRegCtlFromReg]{
  \{P \ast r_s \mapsto_{r}\{q\}  \textsf{ rvs}  \}_{\textsf{rvs}} \overline{is}
}{
  \{P \ast r_s \mapsto_{r}\{q\}  \textsf{ rvs}   \}_{\textsf{rtv}}
  \textsf{mov}~\textsf{cr3},~r_s;\;\overline{is}
  %\lstinline|mov %cr3, r| 
}\\
\inferrule[WriteToRegCtlFromRegModal]{
  \{[\textsf{rtv}](P \ast \mathcal{I}\textsf{ASpace})\ast \mathcal{I}\textsf{ASpace} \ast R\ast r_s \mapsto_{r}\{q\}  \textsf{ rvs}  \}_{\textsf{rvs}} \overline{is}
}{
  \{P \ast \mathcal{I}\textsf{ASpace} \ast [\textsf{rvs}](R \ast\mathcal{I}\textsf{ASpace})\ast r_s \mapsto_{r}\{q\}  \textsf{ rvs}   \}_{\textsf{rtv}}
  \textsf{mov}~\textsf{cr3},~r_s;\;\overline{is}
  %\lstinline|mov %cr3, r| 
}\\
\inferrule[WriteToRegFromRegCtl]{
  \{P \ast r_d \mapsto_{r} \textsf{rvs} \ast r_s \mapsto_{r}\{q\} \textsf{ rvs} \}_{\textsf{rtv}}\;\overline{ is}
}{
  \{P \ast r_d \mapsto_{r} \textsf{rvd} \ast r_s \mapsto_{r}\{q\} \textsf{ rvs} \}_{\textsf{rtv}}
  \textsf{ mov}~\textsf{r}_d,~\textsf{r}_s;\;\overline{is}
  %\lstinline|mov %cr3, r| 
}
\end{mathpar}
\todo[inline]{update for rip tracking}
\caption{Reasoning Rules for Selected \textsf{AMD64} Instructions under}
\label{fig:wpdamd}
\end{figure}

>>>>

\begin{figure}
\begin{mathpar}
%  \inferrule[AddRegImm]{
%  \{P \ast r_d \mapsto_{r} \textsf{rvs} \ast r_s \mapsto_{r}\{q\} \textsf{ rvs} \}_{\textsf{rtv}}\;\overline{ is}
%}{
%  \{P \ast r_d \mapsto_{r} \textsf{rvd} \ast r_s \mapsto_{r}\{q\} \textsf{ rvs} \}_{\textsf{rtv}}
%  \textsf{ mov}~\textsf{r}_d,~\textsf{r}_s;\;\overline{is}
%  \lstinline|mov %cr3, r| 
%}
%\\
% \inferrule[WriteToPhysMemFromReg]{
%   \{P \ast r_s \mapsto_{r}\{q\}  \textsf{rvs}  \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{t}} \textsf{v} \}_{\textsf{rtv}}\;\overline{ is}  
% }{
%   \{P \ast r_s \mapsto_{r}\{q\}  \textsf{rvs}   \ast r_a \mapsto_{r}\{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{t}} \textsf{rvs} \}_{\textsf{rtv}}
%   \textsf{ mov}~[\textsf{r}_a],~\textsf{r}_s;\;\overline{is}
% }
% \\
% \inferrule[WriteToRegFromPhysMem]{
%   \{P \ast r_d \mapsto_{r}  \textsf{v} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{t}} \textsf{v} \}_{\textsf{rtv}}\;\overline{is}
% }{
%   \{P \ast r_d \mapsto_{r}  \textsf{rvd} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{t}} \textsf{v} \}_{\textsf{rtv}}
%   \textsf{mov}~\textsf{r}_d,~[\textsf{r}_a];\;\overline{is}
% }
% \\
\inferrule[WriteToRegFromVirtMem]{
  \{P \ast \mathcal{I}\textsf{ASpace}\ast \mathcal{I}\textsf{ASpace} \ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{iv + x} \ast \ulcorner x = 3 \lor x =4 \urcorner \ast r_d \mapsto_{r}  \textsf{v} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v,rtv}} \textsf{v} \}_{\textsf{rtv}}\;\overline{is}
}{
  \{P \ast \mathcal{I}\textsf{ASpace}\ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{iv} \ast r_d \mapsto_{r}  \textsf{rvd} \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{v} \}_{\textsf{rtv}}\;
  \textsf{mov}~\textsf{r}_d,~[\textsf{r}_a];\;\overline{is}
}
\\
\inferrule[WriteToVirtMemFromReg]{
  \{P \ast \mathcal{I}\textsf{ASpace}\ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{iv + x} \ast \ulcorner x = 3 \lor x =4 \urcorner \ast r_s \mapsto_{r}\{q\}  \textsf{rvs}  \ast r_a \mapsto_{r} \{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{v} \}_{\textsf{rtv}}\;\overline{ is}  
}{
  \{P \ast \mathcal{I}\textsf{ASpace}\ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{iv} \ast r_s \mapsto_{r}\{q\}  \textsf{rvs}   \ast r_a \mapsto_{r}\{q\} \textsf{ vaddr} \ast \textsf{vaddr} \mapsto_{\textsf{v}} \textsf{rvs} \}_{\textsf{rtv}}
  \textsf{ mov}~[\textsf{r}_a],~\textsf{r}_s;\;\overline{is}
}
\\
%\inferrule[WriteToRegCtlFromReg]{
%  \{P \ast r_s \mapsto_{r}\{q\}  \textsf{ rvs}  \}_{\textsf{rvs}} \overline{is}
%}{
%  \{P \ast r_s \mapsto_{r}\{q\}  \textsf{ rvs}   \}_{\textsf{rtv}}
%  \textsf{mov}~\textsf{cr3},~r_s;\;\overline{is}
  %\lstinline|mov %cr3, r| 
%}\\
\inferrule[WriteToRegCtlFromRegModal]{
  \{[\textsf{rtv}](P \ast \mathcal{I}\textsf{ASpace})\ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{iv + 4} \ast \mathcal{I}\textsf{ASpace} \ast R\ast r_s \mapsto_{r}\{q\}  \textsf{ rvs}  \}_{\textsf{rvs}} \;\overline{is}
}{
  \{P \ast \mathcal{I}\textsf{ASpace} \ast \textsf{rip} \mapsto_{\textsf{r}} \textsf{iv} \ast [\textsf{rvs}](R \ast\mathcal{I}\textsf{ASpace})\ast r_s \mapsto_{r}\{q\}  \textsf{ rvs}   \}_{\textsf{rtv}} \;
  \textsf{mov}~\textsf{cr3},~r_s;\;\overline{is}
  %\lstinline|mov %cr3, r| 
}\\
\inferrule[WriteToRegFromRegCtl]{
  \{P \ast  \textsf{rip} \mapsto_{\textsf{r}} \textsf{iv + 4} \ast r_d \mapsto_{r} \textsf{rvs} \ast r_s \mapsto_{r}\{q\} \textsf{ rvs} \}_{\textsf{rtv}}\;\overline{ is}
}{
  \{P \ast  \textsf{rip} \mapsto_{\textsf{r}} \textsf{iv} \ast r_d \mapsto_{r} \textsf{rvd} \ast r_s \mapsto_{r}\{q\} \textsf{ rvs} \}_{\textsf{rtv}}
  \textsf{ mov}~\textsf{r}_d,~\textsf{r}_s;\;\overline{is}
  %\lstinline|mov %cr3, r| 
}
\end{mathpar}
\todo[inline]{update for rip tracking}
\caption{Reasoning Rules for Selected \textsf{AMD64} Instructions under}
\label{fig:wpdamd}
\end{figure}
